---
title: "2020 Google Code Jam - Qualification Round"
output:
  html_notebook:
    theme: sandstone
    toc: yes
    toc_float:
      collapsed: yes
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(root.dir = "")
library(reticulate)
use_python("C:/ProgramData/Anaconda3")
```

## The Problems

All of the problems can be found here:
[Google Code Jam 2020 - Qualification Round](https://codingcompetitions.withgoogle.com/codejam/round/000000000019fd27)


### notes before submission

For R, all input names must be updated to `"stdin"` before submission.
```{r, eval = FALSE}
## in this doc
input <- file("q1_input.txt", "r")

## for submission
input <- file("stdin", "r")
```


<br/>
<br/>

For python3, all the `f` assignments can be removed before submission and all the `f.readline()` should be replaced with `input()`.
```{python, eval = FALSE}
## in this doc
f = open("q1_input.txt", "r")
t = int(f.readline()) 

## for submission
t = int(input()) 
```



### notes before test mode
Sample inputs provided here can be used directly in test mode in google's console.


## Problem 1: Vestigium {.tabset .tabset-fade .tabset-pills}

### R Solution

Fairly straight forward approach leveraging a custom function for checking for dupes.


```{r problem_1}

has_repeat <- function(v) {
  length(v) != length(unique(v))
}

str_2_vect <- function(s) {
  as.integer(unlist(strsplit(s, " ")))
}

input <- file("q1_input.txt", "r")

t <- as.integer(readLines(input, n = 1))

for (i in 1:t) {
  
  n <- as.integer(readLines(input, n = 1))
  
  m <- list()
  
  out_r <- 0
  out_c <- 0
  
  for (j in 1:n) {
    m[[j]] <- str_2_vect(readLines(input, n = 1))
    out_r <- out_r + has_repeat(m[[j]])
  }
  
  m <- matrix(unlist(m), ncol = n, byrow = TRUE)
  
  out_k <- sum(diag(m))
  
  for (col in 1:n) {
    out_c <- out_c + has_repeat(m[, col]) 
  }
  
  cat(paste0("Case #", i, ":"), out_k, out_r, out_c, "\n")
  
}

```


### Sample Data Set
```{r problem_1_input}

input <- file("q1_input.txt", "r")
while(length(line <- readLines(input, n=1)) > 0) {
  cat(line, "\n")
}

```

## Problem 2: Nesting Depth {.tabset .tabset-fade .tabset-pills}

Replace each instance of the number with the number surrounded by an equivalent sets of parantheses (e.g. `1` --> `(1)`, and `2` --> `((2))`), then replace all the `)(` until there's no more.  

### R Solution
```{r problem_2}

str_2_vect <- function(s) {
  as.integer(unlist(strsplit(s, "")))
}


input <- file("q2_input.txt", "r")

t <- as.integer(readLines(input, n = 1))

for (i in 1:t) {
  s <- readLines(input, n = 1)
  v <- unique(str_2_vect(s))
  
  for (j in v[v > 0]) {
    withp <- paste0(paste0(rep("(", j), collapse = ""), 
                    j, 
                    paste0(rep(")", j), collapse = ""))
    s <- gsub(j, withp, s)
  }
  
  while (grepl("[)][(]", s)) {
    s <- gsub("[)][(]", "", s)
  }
  
  cat(paste0("Case #", i, ":"), s, "\n")
  
}

```


### Sample Data Set
```{r problem_2_input, warning = FALSE}

input <- file("q2_input.txt", "r")
while(length(line <- readLines(input, n=1)) > 0) {
  cat(line, "\n")
  # process line
}

```

## Problem 3: Parenting Partnering Returns {.tabset .tabset-fade .tabset-pills}

Sort the tasks by start time and then assign them sequentially. Unfortunately R is slow so the same exact solution had to be rewritten in python 3 to meet the time limit (rip R).

### R solution

```{r problem_3}
          
str_2_df <- function(s) {
  a <- as.integer(unlist(strsplit(s, " ")))
  data.frame(tasknum = j, start = a[1], end = a[2])
}

input <- file("q3_input.txt", "r")

t <- as.integer(readLines(input, n = 1))

  
for (i in 1:t) {
  
  n <- as.integer(readLines(input, n = 1))
  
  tasks <- data.frame(task = integer(),
                      start = integer(),
                      end = integer())
  
  for (j in 1:n) {
    task <- str_2_df(readLines(input, n = 1))
    tasks <- rbind(tasks, task)
  }
  
  tasks <- tasks[order(tasks$start), ]
  
  out <- rep("", n)
  
  c_cur_end <- 0
  j_cur_end <- 0
  
  for (j in 1:n) {
    if (c_cur_end <= tasks$start[j]) {
      out[tasks$tasknum[j]] <- "C"
      c_cur_end <- tasks$end[j]
    } else if (j_cur_end <= tasks$start[j]) {
      out[tasks$tasknum[j]] <- "J"
      j_cur_end <- tasks$end[j]
    } else {
      out <- "IMPOSSIBLE"
      break
    }
  }
    
  out <- paste0(out, collapse = "")
  
  cat(paste0("Case #", i, ":"), out, "\n")
  
}

```

### Python Solution


```{python}
import numpy as np

f = open("q3_input.txt", "r")

t = int(f.readline()) 

dtype = [('tasknum', int), ('start', int), ('end', int), ('who', str)]
for i in range(1, t + 1):     
    n = int(f.readline())        
    tasks = np.empty(n, dtype = dtype)
    for j in range(0, n):
        cur_start, cur_end = [int(s) for s in f.readline().split(" ")]
        tasks['tasknum'][j] = j
        tasks['start'][j] = cur_start
        tasks['end'][j] = cur_end
        tasks['who'][j] = ""
        
    tasks = np.sort(tasks, order = "start", axis = 0)
    
    out = [None] * n
    c_cur_end = 0
    j_cur_end = 0
    
    for j in range(0, n):
        if c_cur_end <= int(tasks[j][1]):
            out[tasks['tasknum'][j]] = "C"
            c_cur_end = int(tasks[j][2])
        elif j_cur_end <= int(tasks[j][1]):
            out[tasks['tasknum'][j]] = "J"
            j_cur_end = int(tasks[j][2])
        else:
            out = "IMPOSSIBLE"
            break
            
    print("Case #{}: {}".format(i, ''.join(out)))   
```


### Sample Data Set
```{r problem_3_input, warning = FALSE}

input <- file("q3_input.txt", "r")
while(length(line <- readLines(input, n=1)) > 0) {
  cat(line, "\n")
}

```
